### 2015-07-06 narrative/qos.tex
qos.

\paragraph{Resource Management Background:} There is an important connection between finding the resources that can help fulfill a particular request and the predictability of the performance of that request, both in terms of latency and resolution. This connection is particular important for reads: in very large scale systems, finding a resource to read can be a significant, if not dominant, component of overall read latency. If the search for resources is unbounded, it will be difficult to make any performance predictions.

Locating resources is a typical distributed systems problem. Central solutions are limited in their scalability, especially if they have to track every update. Traditional file systems are good examples for this: most updates to files require updates to their centrally maintained block allocation tables. The opposite of file systems are ``pile'' systems which instead of keeping track of updates search for resources at request time. Pile systems allow very efficient writes because clients can write whereever there is free space and there is very bookkeeping overhead. Furthermore, pile systems have great flexibility for moving resources around, for example to ensure durability. However, reads require a potentially unbounded search, especially if it is not clear whether the resource actually exists. Methods to make searches more efficient without reverting to centralized bookkeeping usually involves some kind of partitioning of the search space and a method to limit the search to a small number of partitions.

>>>>

\paragraph{Resource Management Background:} There is an important connection between finding the resources
that can help fulfill a particular request and the performance predictability of that request, which demands
careful resource management strategies. This connection is particularly important for reading - in very large 
scale systems, finding a resource to read can be a significant, if not dominant, component of overall read 
latency.

Locating resources is a typical distributed systems problem. Centralized solutions are limited in their
scalability, because typically there exists a single entity that tracks every update in the system. 
Traditional file systems are good examples 
for this: most updates to files require updates to their centrally maintained block allocation tables. 
The opposite of file systems are ``pile'' systems, which, instead of keeping track of updates, search for 
resources at request time. Pile systems allow very efficient writes because clients can write whereever
there is free space and there is very low bookkeeping overhead. Furthermore, pile systems have great
flexibility for moving resources around, for example to ensure durability. However, reads require a 
potentially unbounded search, especially if it is not clear whether the resource actually exists. 
Methods to make searches more efficient without reverting to centralized bookkeeping usually involves 
some kind of partitioning of the search space and a method to limit the search to a small number of partitions.
